#Data analyses and figure creation for the Change Blindness Experiment

###Stacie Heiberg

##Introduction

This file was used to analyze data from my
[Change Blindness](https://www.youtube.com/watch?v=k0lT596YOX0).
All materials including consent, experimental tasks, and debriefing can
be accessed following the previous link and following the links embedded
within the video.

These data represent observations from 46 participants who reported
participating in existing conditions and emailed me their data.Two reported seeing a change that did not happen and two reported seeing a change before there was a change. All four were excluded from the data. 

Two variables were included in the data, the condition, and if the participant saw a change. 

##Preparing data for analysis

First we need to read in the data.

```{r}
results<-read.csv("results.csv")
```
```

##Primary Analysis

In order to see if emotion effected if a participant was more or less likely to experience change blindness, I used a table and a chi-square test. 
```{r}
table(results$Condition,results$Change)
chisq.test(results$Condition,results$Change)
```
The data has a p-value of .66. Emotion did not effect the frequency that change blindness occred in this experiment. 